\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.25in}

% Section formatting
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{0.7em}{0.5em}

\setlength{\parskip}{0.35em}
\setlength{\parindent}{0pt}

% Custom itemize spacing
\setlist[itemize]{itemsep=0.1em, leftmargin=1em}

\begin{document}

\begin{center}
    {\LARGE \textbf{Richard Álvarez}}\\[0.8em]
    Chicago, IL | \href{mailto:rawalvarez731@gmail.com}{rawalvarez731@gmail.com} | (773) 469-9726
\end{center}

\section*{Professional Summary}
Creative videographer with experience in video editing, post-production, and storytelling. Proficient in producing high-quality audiovisual content, managing pre-production planning, on-site shoots, and post-production workflows. Skilled in Adobe Creative Suite, with a passion for crafting visually compelling narratives that align with brand objectives. Eager to expand expertise in multimedia production for marketing and educational purposes.

\section*{Software Proficiency}
Adobe Premiere Pro, DaVinci Resolve, Adobe After Effects, Adobe Photoshop, Audacity

\section*{Education}
\textbf{Kenyon College}, Gambier, OH\\
Bachelor of Arts in Film | Minor: History | Graduation: May 2024\\
Relevant Courses: Senior Seminar in Film, Advanced Post-Production, Directing for the Camera, Digital Photography, Elements and Theory of Post Production

\section*{Professional Experience}
\textbf{Video Editor}, \textit{Performing the Primitive} \hfill May 2022 -- Aug 2022 \\
Edited documentary footage for Sam Pack, ensuring cohesive storytelling and technical quality. Enhanced final product through precise editing, color grading, and sound mixing in Adobe Premiere Pro.

\textbf{IT Assistant}, \textit{Library and Information Services, Kenyon College} \hfill Sep 2023 -- Feb 2024\\
Prepared and maintained AV equipment for classrooms and campus events. Conducted technical checks to ensure reliable operations and developed scheduling tools to optimize workflows.

\textbf{Production Assistant}, \textit{Shopping for Superman} \hfill Jan 2024\\
Assisted in managing production schedules and on-set logistics. Supported AV setup, including lighting and sound equipment, ensuring smooth filming operations.

\textbf{General Contractor Assistant}, \textit{Sommerlad Construction} \hfill Jun 2023 -- Aug 2023\\
Supported various construction tasks and project coordination. Adhered to strict deadlines and safety standards while performing general assembly and setup.

\section*{Independent Projects}
\textbf{Writer, Producer, Director}, \textit{Indiesleaze} \hfill 2024\\
Directed and produced senior thesis film, overseeing all production stages from pre-production through post-production, including editing, sound design, and motion graphics.

\textbf{Script Supervisor}, \textit{Jasmine} \hfill 2023\\
Ensured continuity during filming and maintained detailed notes to align with the script and directorial vision.

\section*{Skills}
\textbf{Video Production}: Pre-production planning, camera operation, audio recording\\
\textbf{Editing Tools}: Adobe Premiere Pro, DaVinci Resolve, After Effects, Audacity\\
\textbf{Graphic Design}: Adobe Photoshop, Canva\\
\textbf{Languages}: English (Fluent), Spanish (Intermediate)

\section*{Extracurricular Activities}
\textbf{Horn Gallery Videographer}, Kenyon College\\
\textbf{Club Basketball Participant}, Kenyon College

\end{document}
