\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{To Hiring Team \\ Production House Chicago \\ Chicago, Illinois}
\opening{Dear Hiring Team,}

I am excited to apply for the Assistant Video Editor position at Production House Chicago. With a Bachelor of Arts in Film from Kenyon College and years of experience editing and producing video content for local Chicago artists, I bring both technical expertise and a passion for storytelling to your team. Working in a professional production house has long been a personal goal, and I am deeply committed to contributing meaningfully to your creative projects.

My liberal arts education across in History, Anthropology, and English has shaped me into a critical thinker with the ability to analyze complex issues and interrogate seemingly simple ideas. These skills have translated directly into my editing work, particularly in crafting compelling narratives from interviews and raw footage. For instance, while editing the documentary Performing the Primitive (2023) by Sam Pack, I identified and highlighted key moments in interviews that drove the story forward, ensuring both clarity and emotional resonance.

Highlights of my qualifications include:
\begin{itemize}
    \item Proficiently editing interviews to distill meaningful sound bites and weave them into cohesive narratives.
    \item Organizing and managing raw footage for projects spanning over 200 hours of material.
    \item Applying advanced editing techniques, including basic color correction and sound leveling, to produce visually compelling stories.
\end{itemize}

This role represents the perfect blend of my creative and professional aspirations. Being part of a collaborative studio environment, especially one rooted in Chicago’s vibrant storytelling scene, aligns with my passion for amplifying voices through documentary-style filmmaking. My experience editing for local artists and my academic background in critical analysis position me to contribute unique value to your team.

I would welcome the opportunity to bring my experience and enthusiasm to Production House Chicago. My resume and portfolio are attached, and I am happy to provide further details about my projects. I look forward to discussing how I can support your team’s vision.

Thank you for considering my application.

\closing{Sincerely,}

Ricky Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}