\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.25in}

% Section formatting
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{0.7em}{0.5em}

\setlength{\parskip}{0.35em}
\setlength{\parindent}{0pt}

% Custom itemize spacing
\setlist[itemize]{itemsep=0.1em, leftmargin=1em}

\begin{document}

\begin{center}
    {\LARGE \textbf{Richard Alvarez}}\\[0.8em]
    Chicago, IL | rawalvarez731@gmail.com | (773) 469-9726 | raulduke.com
\end{center}

\section*{Professional Summary}
Experienced video editor with a strong foundation in narrative storytelling, post-production workflows, and collaborative film production. Skilled in Adobe Premiere Pro, DaVinci Resolve, and After Effects, with a portfolio spanning documentaries, music videos, and narrative shorts.

\section*{Professional Experience}

\textbf{Editor} \\
\textit{Indiesleaze} (2024) \\
Directed and edited senior thesis film, managing narrative structure and visual consistency.

\textit{Performing the Primitive} (2023) \\
Edited documentary footage for Sam Pack, ensuring narrative cohesion and technical quality.

\textit{Summer Legal Scholar Recaps} (2022) \\
Produced professional video content for Ric Sheffield, refining footage for clarity and engagement.

\vspace{0.5em} % Space between roles

\textbf{Music Video Editor} \\
\textit{trees} by GRAYS (2023) \\
Handled post-production, including color grading and sound synchronization.

\textit{Live, Laugh, Kill} by JvneBvg (2022) \\
Managed post-production workflow, ensuring timely project delivery.

\textit{Rick and Morty} by Black Yoshi (2021) \\
Delivered creative edits, emphasizing narrative and comedic elements.

\textit{Poltergeist} by 5ouley (2021) \\
Collaborated with the artist to develop visual style and pacing.

\textit{No Rulez} by InVoid (2021) \\
Applied dynamic editing techniques to synchronize visuals with music.

\textit{Ghosts} by Undercurrent (2020) \\
Edited music video, enhancing rhythm and story through visual cuts.

\vspace{0.5em} % Space between roles

\textbf{Script Supervisor} \\
\textit{Jasmine} (2023) \\
Maintained narrative and technical consistency on set.

\vspace{0.5em} % Space between roles

\textbf{Production Assistant} \\
\textit{Shopping for Superman} (2024) \\
Assisted on-set logistics and maintained production schedules.

\section*{Education}
\textbf{Kenyon College}, Gambier, OH\\
Bachelor of Arts in Film | Minor: History | Graduation: May 2024\\
Relevant Courses: Senior Seminar in Film, Advanced Post-Production, Directing for the Camera, The American Film Industry, Dramatic Structure for Film, Digital Photography, Elements and Theory of Post Production.

\section*{Skills}
\textbf{Editing}: Proficient in Premiere Pro, DaVinci Resolve, After Effects\\
\textbf{Graphic Design}: Skilled in Photoshop for content creation\\
\textbf{Videography}: Experienced in camera operation, lighting, and audio setup

\end{document}
