\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust the page margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\begin{document}

\begin{letter}{Witherite Law Group \\
Chicago, IL}

\opening{Dear Hiring Team,}

I am thrilled to apply for the Videographer position at Witherite Law Group. Your commitment to putting people first and delivering unmatched expertise resonates strongly with my own values as a creative professional. I am excited about the opportunity to contribute my storytelling and technical skills to support your legal and marketing objectives.

During my time at Kenyon College, I had the privilege of creating professional video content for Ric Sheffield, where I produced polished recaps of his Summer Legal Scholar program. This role required me to distill complex concepts into engaging narratives, capturing interviews, and incorporating clear visual elements to ensure his message resonated with his audience. My ability to manage every stage of production—from planning and on-location shooting to post-production—helped deliver high-quality assets that met his expectations.

In addition, as a Film major with hands-on experience in video production, I have developed strong skills in capturing high-quality footage, setting up lighting for diverse environments, and conducting professional, engaging interviews. Whether editing my senior thesis film or managing post-production for Ric Sheffield’s projects, I focus on crafting compelling visuals that align with the goals of the project.

While I am still gaining familiarity with tools like AutoCAD and Revit, I am proficient in Adobe Premiere Pro, After Effects, and DaVinci Resolve, and I am eager to expand my expertise in multimedia tools to meet Witherite’s high standards. My passion for visual storytelling, attention to detail, and ability to work collaboratively make me confident I can bring value to your team.

I am particularly drawn to the opportunity to create educational and promotional videos that positively impact your clients and community. I admire Witherite’s dedication to providing excellent service, and I would be proud to contribute to your mission of helping individuals navigate complex situations with clarity and confidence.

Thank you for considering my application. I look forward to the opportunity to discuss how my skills and experience align with this role.

\vspace{1em}

Sincerely, \\
Ricky Alvarez \\
(773) 469 9726 \\
rawalvarez731@gmail.com \\
Chicago, Illinois

\end{letter}
\end{document}
\textsl{•}