\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fontspec}

\setmainfont{Avenir}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.25in}

% Section formatting
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{0.7em}{0.5em}

\setlength{\parskip}{0.35em}
\setlength{\parindent}{0pt}

% Custom itemize spacing
\setlist[itemize]{itemsep=0.1em, leftmargin=1em}

\begin{document}

\begin{center}
    {\LARGE \textbf{Richard Alvarez}}\\[0.8em]
    Chicago, IL | rawalvarez731@gmail.com | (773) 469-9726
\end{center}

\section*{Professional Summary}
Aspiring filmmaker passionate about storytelling and crafting professional visual experiences. Experienced in video editing, videography, and collaborative film production, with a focus on high-quality content and creative workflows. Skilled in project management and team coordination.

\section*{Software Proficiency}
Adobe Premiere Pro, DaVinci Resolve, Adobe Photoshop, Adobe After Effects

\section*{Education}
\textbf{Kenyon College}, Gambier, OH\\
Bachelor of Arts in Film | Minor: History | Graduation: May 2024\\
Relevant Courses: Senior Seminar in Film, Advanced Post-Production, Directing for the Camera, The American Film Industry, Dramatic Structure for Film, Digital Photography, Elements and Theory of Post Production.

\section*{Professional Experience}
\textbf{Editor}, \textit{Performing the Primitive} (2023)\\
Edited documentary footage for Sam Pack, ensuring narrative cohesion and technical quality.

\textbf{Editor}, \textit{Summer Legal Scholar Recaps} (2022)\\
Produced professional video content for Ric Sheffield, refining footage for clarity and engagement.

\textbf{Production Assistant}, \textit{Shopping for Superman} (2024)\\
Supported production schedules and on-set operations.

\section*{Independent Projects}
\textbf{Writer, Producer, Director}, \textit{Indiesleaze} (2024)\\
Directed and produced senior thesis film, managing all stages of production.

\textbf{Script Supervisor}, \textit{Jasmine} (2023)\\
Ensured continuity and adherence to the script during production.

\section*{Music Videos}
\textbf{Editor and Director}
\vspace{-0.8em}
\begin{itemize}
    \item \textit{Ghosts} by Undercurrent (2020)
    \item \textit{No Rulez} by InVoid (2021)
    \item \textit{Poltergeist} by 5ouley (2021)
    \item \textit{Rick and Morty} by Black Yoshi (2021)
    \item \textit{Live, Laugh, Kill} by JvneBvg (2022)
    \item \textit{trees} by GRAYS (2023)
\end{itemize}

\section*{Skills}
\textbf{Editing}: Proficient in Premiere Pro, DaVinci Resolve, After Effects\\
\textbf{Graphic Design}: Skilled in Photoshop for content creation\\
\textbf{Videography}: Experienced in camera operation, lighting, and audio setup

\end{document}